\begin{englishabstract}
Brain-computer interface (BCI) IoT links carry both highly sensitive neural data and control commands, and are exposed to replay, tampering, man-in-the-middle (MITM), and traffic-fingerprinting attacks. Although TLS/DTLS are cryptographically mature, practical deployment on constrained devices and restricted public networks still faces engineering trade-offs in resource cost, reachability, and traffic observability. This thesis studies the IoT\_BCI-Sudoku protocol implemented in this repository and evaluates a combined design of authenticated handshake, AEAD record protection, and Sudoku-based appearance transformation against Pure-AEAD, DTLS, MQTT/TLS, and CoAP/UDP under a unified benchmarking methodology.

The protocol is implemented as an enhancement layer between application and TCP. The handshake uses Ed25519 certificates, X25519 key agreement, transcript binding, and confirmation MAC; the session layer adopts AEAD records; the outer appearance layer provides reversible byte mapping, randomized padding, ASCII layout mode, and customizable byte-pattern templates. To ensure reproducibility, we build a three-stage evidence pipeline: local baseline benchmarking, fingerprinting and attack validation, and cross-region Internet benchmarking, with field-level traceability from figures/tables to raw evidence files.

Results show that in the cross-region restricted network, Sudoku-pure and Sudoku-packed achieve 108.676 ms and 105.536 ms average RTT, comparable to DTLS (109.040 ms) and lower than MQTT/TLS (150.072 ms). Their data-plane memory metric is 2712 B and 2936 B, substantially below DTLS (185472 B) and MQTT/TLS (97680 B). Fingerprinting accuracy reaches 96.67\%. For synthetic BCI classes, recovery is 1.0000 without padding and drops to 0.1667 with padding. In the TLS MITM baseline, recovery rate is 1.0, while Sudoku replay/tampering scenarios are consistently rejected. These findings indicate that Sudoku provides a quantifiable engineering balance among security, efficiency, and fingerprint resistance: pure mode prioritizes obfuscation strength, whereas packed mode prioritizes bandwidth efficiency.

The thesis contributes a closed loop from mathematical modeling to implementation and evidence-based validation, and explicitly reports both strengths and limitations against mainstream baselines. The results provide a practical reference for protocol selection and future standardization in BCI-IoT secure communication.

\englishkeyword{BCI, IoT, secure communication, traffic fingerprinting, anti-replay, protocol benchmarking, Sudoku}
\end{englishabstract}
